Investigating shape standardization using geometric morphometry of pottery from Iron Age northeastern Taiwan

### 2020-04-11 analysis/paper/paper.Rmd
add phase column to MANOVA table

manv <- rrtools:::quietly ( MANOVA_PW(op.p, "phase") ) 
su_manv <- as.data.frame(manv$summary)

su_manv_tab <- 
  su_manv %>% 
  mutate_all(round, 4) %>% 
  select(-Df, -`num Df`) %>% 
  rename(`Pillai's trace` = Pillai,
         `Approximate F value` = `approx F`,
         `degrees of freedom` = `den Df`)

>>>>

manv <- rrtools:::quietly ( MANOVA_PW(op.p, "phase") ) 
su_manv <- as.data.frame(manv$summary) %>% 
  rownames_to_column()

su_manv_tab <- 
  su_manv %>% 
  mutate_if(is.numeric, round, 4) %>% 
  select(-Df, -`num Df`) %>% 
  rename(Comnparison = rowname,
         `Pillai's trace` = Pillai,
         `Approximate F value` = `approx F`,
         `degrees of freedom` = `den Df`)
